Clustering: A pipeline to analyse time-course gene expression data

### 2019-03-22 scripts/03_clustering.Rmd
FIX not the same API as normal Kmeans

```{r}
possible_n_clusters = 5:20

@@

# function to compute total within-cluster sum of square 
within_cluster_sum_of_squares = function(n_cluster){
    return(moanin:::splines_kmeans(y, splines_model,
				   n_clusters=n_cluster, random_seed=42,
				   n_init=10)$tot.withinss)
}

>>>>

```{r}
possible_n_clusters = 5:20
```

@@

# function to compute total within-cluster sum of square 
within_cluster_sum_of_squares = function(n_cluster){
    return(moanin:::splines_kmeans(y, splines_model,
				   n_clusters=n_cluster, random_seed=42,
				   n_init=10)$WCSS_per_cluster)
}
